Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
note
first stab at speech community paragraph

TODO: What is a linguistic community.

@@

As a quantitative assessment, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them from the comment-community co-occurence matrix,
using data which spans January 2014 to April 2017. We refer the reader
to \citet{Kumar2018}\jp{I actually cannot find in their paper what
  they do.} for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether and how much a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data. 
%
We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(Figure~\ref{fig:pairwise-comm-sim}).

@@

However we observe that the CCLM perplexity is only weakly correlated with the
indiscernibility to the corresponding latent LMCC
(\cref{fig:cclm_lmcc_ppl}).

\begin{figure}
  \pplscatter{lstm-3-1_cclm}{lstm-3-1_lmcc}
  \caption{%
    Mean linguistic perplexity (x-axis) and community indiscernibility
    (y-axis) per community (Pearson's r = \num{0.30}, p =
    \num{0.0444}).  Shown here for the LSTM model with $c = 1$, but
    other models exhibit similar behavior.  }
  \label{fig:cclm_lmcc_ppl}
\end{figure}

>>>>

The \emph{speech community} is an important concept 
in the study of linguistic variation.
Any social group exhibiting some degree of linguistic idiosyncrasy
may be considered a speech community \citep{Gumperz1972}.
Linguistic communication requires that participants share 
\emph{common ground} \citep{Stalnaker2002} knowledge of certain norms, 
including the meaning of words, syntactic structure, and patterns of interaction.
Speakers often assume that these norms are common ground based on joint membership
in some community \cite{Clark1996}.

This basis allows for variation in linguistic convention accross communities.

@@

As a quantitative assessment, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them from the message-community co-occurence matrix,
using data which spans January 2014 to April 2017. We refer the reader
to \citet{Kumar2018}\jp{I actually cannot find in their paper what
  they do.} for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether and how much a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data. 
%
We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(Figure~\ref{fig:pairwise-comm-sim}).

@@

However we observe that the CCLM perplexity is only weakly correlated with the
indiscernibility to the corresponding latent LMCC
(\cref{fig:cclm_lmcc_ppl}).
\jp{actually, if we had many more communities, then the lines could be ``more blurred'' between various communities, and we may have a stronger correlation here.}
\begin{figure}
  \pplscatter{lstm-3-1_cclm}{lstm-3-1_lmcc}
  \caption{%
    Mean linguistic perplexity (x-axis) and community indiscernibility
    (y-axis) per community (Pearson's r = \num{0.30}, p =
    \num{0.0444}).  Shown here for the LSTM model with $c = 1$, but
    other models exhibit similar behavior.  }
  \label{fig:cclm_lmcc_ppl}
\end{figure}
